### 2021-05-14 article/article.tex
update

\usepackage{physics,amsmath, amsfonts, siunitx, amssymb, graphicx, subcaption}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\begin{document}
%TODO: nsi intro, clear about factor 3
\section{Detector formalism}
The neutrino flux at the detector is calculated by propagating the atmospheric neutrino flux~\cite{hondapaper} through the Earth by solving the 
Schrödinger equation for varying density. The Earth density profile is taken from the PREM~\cite{PREM}. The baseline for a given trajectory is determined using an average neutrino
production height of 15 km and an Earth radius of 6371 km. %TODO: add more here? no neutrino absorption

@@

\subsection{IceCube}\label{ch:ICmethod}
The event rate for each bin reads
\begin{align}\label{eq:ICevents}
   N_{ij} &= T\sum_\beta \int_{(\cos{\theta_z^r})_i}^{(\cos{\theta_z^r})_{i+1}} \dd \cos{\theta^r_z} \int_{E^r_{j}}^{E^r_{j+1}} \dd E^r \int_0^\pi R(\theta^r,\theta^t) \dd \cos{\theta^t} \int_0^\infty \phi_\beta^\text{det}  A^\text{eff} R(E^r,E^t) 
   \dd E^t\,,
\end{align}
where $T$ is the live time of the detector, and $A^\text{eff}$ its effective area averaged over the flavors $\beta$ from~\cite{ICaeff}. $R(x^r,x^t)$ is a resolution function, 
which is responsible for the smearing between the reconstructed and true parameters $x^r$ and $x^t$, respectively. We assume a log-normal distribution, giving it the form 
\begin{align}
    R(x^r, x^t) = \frac{1}{\sqrt{2\pi} \sigma_{x^r}x^r} \exp\left[-\frac{(\log x^r-\mu(x^t))^2}{2\sigma_{x^r}^2}\right]\,.
\end{align}
However, the energy reconstruction is biased~\cite{weaverEvidenceAstrophysicalMuon}, which means that we don't make the assumption that $\mu(E^t) =E^r$. To model this relationship between $\Etrue$ and $\Ereco$, we train a Gaussian process regressor on the dataset~\cite{IC2016}, from which
we can extract a predicted mean and standard deviation for a given $E^{reco}$. We then take the $\Etrue$ points of the 99th percentile of each distribution to obtain
the limits of $\Etrue$ at which to integrate over. We have no angular resolution function since the angle resolution in IceCube for track-like events is less than $\SI{2}{\degree}$, making $\ztrue$ coincide with $\zreco$ for our study. 
The data is from the 86 string sterile analysis~\cite{IC2020}.

@@

We plot the event pull $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ where $N_{SI}$ $(N_{NSI})$ are the numbers of expected events
assuming standard (non-standard) interactions in Fig.~\ref{fig:event_pulls}. This gives the normalized difference in the
number of expected events at the detector, and illustrates the expected sensitivity of DeepCore for the NSI parameters.

@@

\section{Results}
%Short intro
\subsection{Methodology}
For our analyses, we define our $\chi^2$ as
\begin{align} \label{eq:chisq}
    \chi^{2}(\hat{\theta},\alpha,\beta, \kappa)=\sum_{ijk} \frac{\left(N^\text{th}-N^\text{data}\right)_{ijk}^{2}}
    {\left(\sigma^\text{data}_{ijk}\right)^{2} + \left(\sigma^\text{syst}_{ijk}\right)^{2}}+ 
    \frac{(1-\alpha)^2}{\sigma_\alpha^2} + \frac{\beta^2}{\sigma_\beta^2}\,
\end{align}
where we minimize over the model parameters $\hat{\theta} \in \{\dm, \theta_{23}, \epsilon\}$, the penalty terms $\alpha$ and $\beta$, and the free parameter $\kappa$.
$N_{ijk}^\text{th}$ is the expected number of events from theory, and $N_{ijk}^\text{data}$ is the observed number of events in that bin. We set $\sigma_\alpha = 0.25$ as the atmospheric flux normalization error, and $\sigma_\beta = 0.04$ as the zenith angle slope error~\cite{hondapaper}. 
The observed event number has an associated Poissonian uncertainty $\sigma_{ijk}^\text{data} = \sqrt{N_{ijk}^\text{data}}$.
% Make clear distinction of different sigma syst here.
For IceCube, the event count takes the form
\begin{align}
    N^\text{th}_{ijk} = \alpha\left[1+\beta (0.5 + \zreco_i )\right] N_{ijk}(\hat{\theta})\,,
\end{align}
with $N_{ijk}(\hat{\theta})$ from Eq.~\ref{eq:ICevents}. Here, we allow the event distribution to rotate around the median zenith angle of $\zreco = -0.5$.

For DeepCore and PINGU, and the event count takes the form
\begin{align}
    N^\text{th}_{ijk} = \alpha\left[1+\beta \zreco_i \right] N_{ijk}(\hat{\theta}) + \kappa N_{ijk}^{\mu_{atm}}\,,
\end{align}
with $N_{ijk}(\hat{\theta})$ from Eq.~\ref{eq:MCevents}. $N_{ijk}^{\mu_{atm}}$ is the muon background, which is left to float freely in the DeepCore analysis.
The background at PINGU can be considered neglible to first order~\cite{PINGUdata}, and we thus put $\kappa=0$ when calculating the PINGU $\chi^2$\,. 
Since the median zenith is $\zreco = 0$ for DeepCore and PINGU, we allow the event count to rotate around zero.
For IceCube, we set $\sigma_{ijk}^\text{syst} = f\sqrt{N_{ijk}^\text{data}}$. %TODO: and take ... %.
For DeepCore, we use the provided systematic error distribution which accounts for both uncertanties in the finite MC statistics and in the data-driven 
muon background estimate~\cite{DC2019data}. %TODO segue

@@

%TODO: ploit contour for ett-emt
 \begin{table}
   \begin{center}
   \begin{tabular}{lcc}
           \hline \hline \\
           Parameter & 90\% CL & $3\sigma$  \\
           \hline \multicolumn{3}{c} {\hspace{1.5cm} DeepCore }  \\[0.1em]
           $\ett$ & [-0.029, 0.044]\hspace{1cm} & [-, -] \\
           $\emt$ & [-0.015, 0.005]\hspace{1cm} & [-, 0.015] \\
           $\eem$ & [-0.072, 0.075]\hspace{1cm} & [-0.132, 0.127]\\
           $\eet$ & [-0.074, 0.141]\hspace{1cm} & [-0.174, 0.2  ]\\\\
           \multicolumn{3}{c} {\hspace{1.5cm} PINGU } \\
           $\ett$ & [-0.033, -]\hspace{1cm} & [-0.048, -] \\
           $\emt$ & [-0.007, 0.007]\hspace{1cm} & [-0.011, 0.013] \\
           $\eem$ & [-0.062, 0.057]\hspace{1cm} & [-0.122, 0.103] \\
           $\eet$ & [-0.069, 0.077]\hspace{1cm} & [-0.121, 0.133] \\\\
           \multicolumn{3}{c} {\hspace{1.5cm} DeepCore + PINGU } \\
           $\ett$ & [-0.028, 0.043]\hspace{1cm} & [-0.043, -]\\
           $\emt$ & [-0.007, 0.005]\hspace{1cm} & [-0.011, 0.01] \\
           $\eem$ & [-0.048, 0.048] \hspace{1cm} & [-0.09, 0.085]\\
           $\eet$ & [-0.054, 0.072] \hspace{1cm} & [-0.101, 0.118] \\
           \hline
           \hline
   \end{tabular}
   \end{center}
   \caption{DeepCore and PINGU results from the $\Delta \chi^2$ in Fig.~\ref{fig:3D_NO}.}\label{table:DC_PINGU_results}
\end{table}

\begin{table}
   \begin{center}
   \begin{tabular}{lccc}
           \hline \hline & \multicolumn{3}{c} {\text {Best fit}} \\
           \cline { 2 - 4 } Parameter & $\dm$ & $\theta_{23}$  & $\epsilon$  \\
           \hline \multicolumn{3}{c} {\hspace{2.5cm} DeepCore }  \\[0.1em]
           $\ett$ &  2.435 & 47.84 & 0.0125 \\
           $\emt$ &  2.435 & 43.97 & -0.005 \\
           $\eem$ &  2.435 & 43.97 & 0 \\
           $\eet$ &  2.435 & 43.97  & 0.05 \\\\
           \multicolumn{3}{c} {\hspace{2.5cm} IceCube } \\
           $\emt$ &  - & - & - \\
           \hline
           \hline
   \end{tabular}
   \end{center}
   \caption{Best fit points for $\dm$ and $\theta_{23}$ are given in units of $\si{10^{-3}\eV\squared}$ and
   degrees, respectively.}\label{table:bestfit}
\end{table}
%TODO:  include ranges for different f.
%make log table with secyions of dc, p, ic, dc+p
Comparing the PINGU results in Fig.~\ref{fig:PINGU_3D_NO} and the DeepCore results in Fig.~\ref{fig:DC_3D_NO}, we note that 
the best-fit for each NSI parameter for the PINGU experiment is expected to be zero. This is because the `data' we generated during 
the PINGU simulations assumes no NSI since they have yet to be observed in nature. This introduces a non-NSI bias in our joint analysis,
since PINGU has stronger statistics than DeepCore, and will thus pull the joint $\chi^2$ towards $\epsilon =0$.

@@

%TODO: subsection about comparison between different papers. 
\bibliographystyle{elsarticle-num}
\bibliography{article}

>>>>

\usepackage{physics,amsmath, amsfonts, siunitx, amssymb, graphicx, subcaption}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\begin{document}
%TODO: nsi intro, clear about factor 3
\section{Formalism}
\begin{align}
   \mathcal{L}_{\mathrm{NC}} &= -2 \sqrt{2} G_{F} \epsilon_{\alpha \beta}^{f X}\left(\bar{\nu}_{\alpha} \gamma^{\mu} P_{L} \nu_{\beta}\right)\left(\bar{f} \gamma_{\mu} P_{X} f\right)\,,
\end{align}
NC denotes the neutral current interaction with 
$f \in \{e,u,d\}$.

For chirality $X \in \{L,R\}$, the NSI Hamiltonian takes the form 
\begin{align}
   H &= \frac{1}{2E} UM^2U^\dagger + \sqrt{2}G_F n_e \text{diag}(1,0,0) + \sqrt{2}G_F \sum_f n_f \epsilon^{fX}
\end{align}

We have no independent sensitivity for the chirality of $\epsilon^X$, so we sum over these and normalize the fermion number density $n_f$ by
the electron number density $n_e$. Our matter study will be wholly confined to the interior of the Earth, where we assume electrical neutrality and equal distribution of neutrons and protons, 
so $n_u/n_e \simeq n_d/n_e \simeq 3$.
The effective matter NSI parameters now take the form
\begin{align} \label{eq:epsilon}
    \epsilon_{\alpha\beta} &= \sum_X \sum_f \frac{n_f}{n_e} \epsilon^{fX}_{\alpha\beta} \nonumber \\
                           &= \epsilon_{\alpha\beta}^{eV} + 3\epsilon_{\alpha\beta}^{uV} + 3\epsilon_{\alpha\beta}^{dV}
\end{align}
We note that our definition of $\epsilon_{\alpha\beta}$ differs from some texts, where the quark number density is used to normalize
the parameters\cite{deepcoreNSI}.

With the matter potential $V = \sqrt{2}G_F n_e$, we write
\begin{align} \label{eq:H_NSI}
   H &= \frac{1}{2E} UM^2U^\dagger + V\,
   \begin{bmatrix}
      1 + \epsilon_{ee} & \epsilon_{e\mu} & \epsilon_{e\tau}  \\
      \epsilon_{e\mu} & \epsilon_{\mu\mu} & \epsilon_{\mu\tau}  \\
      \epsilon_{e \tau} & \epsilon_{\mu\tau} & \epsilon_{\tau\tau}
  \end{bmatrix}\,,
\end{align}
where we have assumed the components of the NSI matrix to be real.

\section{Detector formalism}
The neutrino flux at the detector is calculated by propagating the atmospheric neutrino flux~\cite{hondapaper} through the Earth by solving the 
Schrödinger equation for varying density. The Earth density profile is taken from the PREM~\cite{PREM}. The baseline for a given trajectory is determined using an average neutrino
production height of 15 km and an Earth radius of 6371 km. The propagation does not include neutrino absorption.
%TODO: add more here? are there more effects than just absoption missing? justify absorption missing?

@@

\subsection{IceCube}\label{ch:ICmethod}
We obtain the data from the IC-86 sterile data release~\cite{IC2020}. The event rate for each bin reads
\begin{align}\label{eq:ICevents}
   N_{ij} &= T\sum_\beta \int_{(\cos{\theta_z^r})_i}^{(\cos{\theta_z^r})_{i+1}} \dd \cos{\theta^r_z} \int_{E^r_{j}}^{E^r_{j+1}} \dd E^r \int_0^\pi R(\theta^r,\theta^t) \dd \cos{\theta^t} \int_0^\infty \phi_\beta^\text{det}  A^\text{eff} R(E^r,E^t) 
   \dd E^t\,,
\end{align}
where $T$ is the live time of the detector, and $A^\text{eff}$ its effective area averaged over the flavors $\beta$ from~\cite{ICaeff}. $R(x^r,x^t)$ is a resolution function, 
which is responsible for the smearing between the reconstructed and true parameters $x^r$ and $x^t$, respectively. We assume a log-normal distribution, giving it the form 
\begin{align}
    R(x^r, x^t) = \frac{1}{\sqrt{2\pi} \sigma_{x^r}x^r} \exp\left[-\frac{(\log x^r-\mu(x^t))^2}{2\sigma_{x^r}^2}\right]\,.
\end{align}
However, the energy reconstruction is biased~\cite{weaverEvidenceAstrophysicalMuon}, which means that we don't make the assumption that $\mu(E^t) =E^r$. To model this relationship between $\Etrue$ and $\Ereco$, we train a Gaussian process regressor on the dataset~\cite{IC2016}, from which
we can extract a predicted mean and standard deviation for a given $E^{reco}$. We then take the $\Etrue$ points of the 99th percentile of each distribution to obtain
the limits of $\Etrue$ at which to integrate over. We take the angular resolution function to be identically unity since the angle resolution in IceCube for track-like events is less than $\SI{2}{\degree}$, making $\ztrue$ coincide with $\zreco$ for our study.

@@

We plot the normalized event difference $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ where $N_{SI}$ $(N_{NSI})$ are the numbers of expected events
assuming standard (non-standard) interactions in Fig.~\ref{fig:event_pulls}. This illustrates the expected sensitivity of DeepCore for the NSI parameters.

@@

\section{Results}
%Short intro
\subsection{Methodology}\label{sec:method}
For our analyses, we define our $\chi^2$ as
\begin{align} \label{eq:chisq}
    \chi^{2}(\hat{\theta},\alpha,\beta, \kappa)=\sum_{ijk} \frac{\left(N^\text{th}-N^\text{data}\right)_{ijk}^{2}}
    {\left(\sigma^\text{data}_{ijk}\right)^{2} + \left(\sigma^\text{syst}_{ijk}\right)^{2}}+ 
    \frac{(1-\alpha)^2}{\sigma_\alpha^2} + \frac{\beta^2}{\sigma_\beta^2}\,
\end{align}
where we minimize over the model parameters $\hat{\theta} \in \{\dm, \theta_{23}, \epsilon\}$, the penalty terms $\alpha$ and $\beta$, and the free parameter $\kappa$.
$N_{ijk}^\text{th}$ is the expected number of events from theory, and $N_{ijk}^\text{data}$ is the observed number of events in that bin. We set $\sigma_\alpha = 0.25$ as the atmospheric flux normalization error, and $\sigma_\beta = 0.04$ as the zenith angle slope error~\cite{hondapaper}. 
The observed event number has an associated Poissonian uncertainty $\sigma_{ijk}^\text{data} = \sqrt{N_{ijk}^\text{data}}$.
For IceCube, the event count takes the form
\begin{align}
    N^\text{th}_{ijk} = \alpha\left[1+\beta (0.5 + \zreco_i )\right] N_{ijk}(\hat{\theta})\,,
\end{align}
with $N_{ijk}(\hat{\theta})$ from Eq.~\ref{eq:ICevents}. Here, we allow the event distribution to rotate around the median zenith angle of $\zreco = -0.5$.

For DeepCore and PINGU, and the event count takes the form
\begin{align}
    N^\text{th}_{ijk} = \alpha\left[1+\beta \zreco_i \right] N_{ijk}(\hat{\theta}) + \kappa N_{ijk}^{\mu_{atm}}\,,
\end{align}
with $N_{ijk}(\hat{\theta})$ from Eq.~\ref{eq:MCevents}. $N_{ijk}^{\mu_{atm}}$ is the muon background, which is left to float freely in the DeepCore analysis.
The background at PINGU can be considered neglible to first order~\cite{PINGUdata}, and we thus put $\kappa=0$ when calculating the PINGU $\chi^2$\,. 
Since the median zenith is $\zreco = 0$ for DeepCore and PINGU, we allow the event count to rotate around zero.

We treat the uncorrelated systematic uncertanties differently for each detector. For IceCube, we set $\sigma_{ijk}^\text{syst} = f\sqrt{N_{ijk}^\text{data}}$. We consider (best) worst-case scenarios in IceCube assuming
$(f=5\%)$, $f=15\%$. For PINGU, we use the same form but instead assume $f=0\%$ and $f=5\%$ for the best and worst-cases respecively. %TODO: maybe source/justification for these values?
For DeepCore, we use the provided systematic error distribution which accounts for uncertanties in the finite MC statistics and in the data-driven 
muon background estimate~\cite{DC2019data}.  %TODO segue

@@

%TODO: ploit contour for ett-emt
{\renewcommand{\arraystretch}{1.3}
 \begin{table}
   \begin{center}
   \begin{tabular}{lcccc}
      \hline \hline \\
      Parameter & Best 90\% CL & Best $3\sigma$ & Worst 90\% CL & Worst $3\sigma$\\
      \hline & \multicolumn{4}{c}{IceCube}  \\
      $\emt$ & [-0.0098, 0.009 ] & [-0.0148, 0.014 ] & [-0.0152, 0.0145] & [-, -] \\\\
      & \multicolumn{4}{c}{DeepCore}  \\[0.3em]
      $\ett$ & [-0.029, 0.045] & [-, -]& [-0.029, 0.045] & [-, -] \\
      $\emt$ & [-0.015, 0.0048] & [-, 0.015]& [-0.015, 0.0048] & [-, 0.015] \\
      $\eem$ & [-0.072, 0.075] & [-0.132, 0.127]& [-0.072, 0.075] & [-0.132, 0.127]\\
      $\eet$ & [-0.074, 0.141] & [-0.174, 0.20  ]& [-0.074, 0.141] & [-0.174, 0.20  ]\\\\
      &\multicolumn{4}{c}{IceCube + DeepCore}  \\
      $\emt$ & [-0.0182,  0.00030] & [-, 0.0104] & [-0.0185, 0.00030] & [-, 0.0104] \\
      \hline
      \hline
   \end{tabular}
   \end{center}
   \caption{IceCube and DeepCore results from the $\Delta \chi^2$ in Fig.~\ref{fig:3D_NO}. IceCube best and worst case refers to 
   the systematic uncertainty scenarios considered as in Sec.~\ref{sec:method}}\label{table:IC_DC_results}
\end{table}
\begin{table}
   \begin{tabular}{lcccc}
      \hline \hline \\
      Parameter & Best 90\% CL & Best $3\sigma$ & Worst 90\% CL & Worst $3\sigma$\\
      \hline & \multicolumn{4}{c}{PINGU} \\
      $\ett$ & [-0.0326, -] & [-0.0482, ] & [-0.0371, -] & [-, -] \\
      $\emt$ & [-0.0065, 0.0071] & [-0.011, 0.013] & [-0.0078, 0.0087] & [-0.0136, 0.0162] \\
      $\eem$ & [-0.062, 0.057] & [-0.122, 0.103] & [-0.1057, 0.0799] & [-0.198, 0.141]\\
      $\eet$ & [-0.069, 0.077] & [-0.121, 0.133] & [-0.1072, 0.1022] & [-0.1805, 0.1633]\\\\
      & \multicolumn{4}{c}{DeepCore + PINGU} \\
      $\ett$ & [-0.028, 0.043] & [-0.043, -] & [-0.0285,  0.0423] & [-0.0447, -]\\
      $\emt$ & [-0.0067, 0.0049] & [-0.0109,  0.0101] & [-0.0049, 0.0086] & [-0.0098, 0.0146]\\
      $\eem$ & [-0.048, 0.048]  & [-0.090, 0.085] & [-0.0721, 0.0503] & [-0.1262, 0.0931]\\
      $\eet$ & [-0.053, 0.072]  & [-0.101, 0.118] & [-0.0901, 0.0624] & [-0.1491, 0.1168]\\\\
      & \multicolumn{4}{c}{IceCube + DeepCore + PINGU}  \\
      $\emt$ & [-0.0088,  0.003 ] & [-0.0128, 0.0081] & [-0.01, 0.0028] & [-0.0145, 0.0087]\\
      \hline
      \hline
   \end{tabular}
   \caption{PINGU and joint results from the $\Delta \chi^2$ in Fig.~\ref{fig:3D_NO}. PINGU best and worst cases refers to 
   the systematic uncertainty scenarios considered as in Sec.~\ref{sec:method}}\label{table:PINGU_joint_results}
\end{table}

\begin{table}
   \begin{center}
   \begin{tabular}{lccc}
           \hline \hline & \multicolumn{3}{c} {\text {Best fit}} \\
           \cline { 2 - 4 } Parameter & $\dm$ & $\theta_{23}$  & $\epsilon$  \\
           \hline \multicolumn{3}{c} {\hspace{2.5cm} DeepCore }  \\[0.1em]
           $\ett$ &  2.435 & 47.84 & 0.0125 \\
           $\emt$ &  2.435 & 43.97 & -0.005 \\
           $\eem$ &  2.435 & 43.97 & 0 \\
           $\eet$ &  2.435 & 43.97  & 0.05 \\\\
           \multicolumn{3}{c} {\hspace{2.5cm} IceCube } \\
           $\emt$ &  2.435 & 51.70 & 0 \\
           \multicolumn{3}{c} {\hspace{2.5cm} IceCube + DeepCore } \\
           $\emt$ &  2.517 & 43.97 & -0.01 \\
           \hline
           \hline
   \end{tabular}
   \end{center}
   \caption{Best fit points for $\dm$ and $\theta_{23}$ are given in units of $\si{10^{-3}\eV\squared}$ and
   degrees, respectively.}\label{table:bestfit}
\end{table}
%TODO:  include ranges for different f.
%make log table with secyions of dc, p, ic, dc+p
Comparing the PINGU results in Fig.~\ref{fig:PINGU_3D_NO} and the DeepCore results in Fig.~\ref{fig:DC_3D_NO}, we note that 
the best-fit for each NSI parameter for the PINGU experiment is expected to be zero. This is because the `data' we generated during 
the PINGU simulations assumes no NSI since they have yet to be observed in nature. This introduces a non-NSI bias in our joint analysis,
since PINGU has stronger statistics than DeepCore, and will thus pull the joint $\chi^2$ towards $\epsilon =0$.

@@

%TODO: subsection about comparison between different papers.

\begin{figure}
   \includegraphics[width=0.9\textwidth]{figures/PINGU_2D_all_f0.pdf}
\end{figure}
\begin{figure}
   \includegraphics[width=0.9\textwidth]{figures/PINGU_2D_all_f5.pdf}
\end{figure}
\bibliographystyle{elsarticle-num}
\bibliography{article}

### 2021-05-14 thesis/tex/nsiTheory.tex
update

We have no independent sensitivity for the neither chirality nor flavor type of $\epsilon^X$, so we sum over these and study the effective matter NSI parameter
 $\epsilon_{\ab}$:
\begin{align}
    \epsilon_{\ab} = \sum_{X \in \{L,R\}} \sum_{f \in \{e,u,d\}} \frac{N_f}{N_e} \epsilon^{fX}_{\ab}\,.
\end{align}
Our matter study will be wholly confined to the interior of the Earth, where we assume electrical neutrality and equal distribution of neutrons and protons, 
we get $N_u/N_e \simeq U_d/N_e \simeq 3$. Also we assume the components $\epsilon_{\a\b}$ to be real. Thus,
\begin{align}
    \epsilon_{\ab} =  \sum_X [\epsilon_{\ab}^{eX} + 3(\epsilon_{\ab}^{uX} + \epsilon_{\ab}^{dX})]
\end{align}
Now, $\epsilon_{\ab}$ enters the Hamiltonian as entries of a potential-like matrix. In Eq.~\ref{eq:NSIH}, $A_{CC}\text{diag}(1,0,0)$ is our 
familiar matter potential from the Standard Model. There is also our new term, $A_{CC} \epsilon$, which contains the components $\epsilon_{\a\b}$:
\begin{align}\label{eq:NSIH}
    H &= \frac{1}{2E} \left[UM^2U^\dagger + A_{CC}\text{diag}(1,0,0) + A_{CC} \epsilon \right] \nonumber \\
      &= \frac{1}{2E} \left[UM^2U^\dagger + A_{CC}
      \begin{pmatrix}
          1 + \epsilon_{ee} & \epsilon_{e\mu} & \epsilon_{e\tau}  \\
          \epsilon_{\mu e} & \epsilon_{\mu\mu} & \epsilon_{\mu\tau}  \\
          \epsilon_{\tau e} & \epsilon_{\tau\mu} & \epsilon_{\tau\tau}
      \end{pmatrix} \right]\,.
\end{align} 
In the limit $\epsilon_{\ab} \to 0$, we recover the standard interaction Hamiltonian from Eq.~\ref{eq:H_3gen}.
We can draw several conclusions from this form of the Hamiltonian. Any nonzero off-diagonal element $\epsilon_{\ab}, \a \neq \b$ will make the NSI violate 
lepton flavor, just as the off-diagonal elements of $U$ does in the SM. Moreover, since the SM potential has the same order in $A_{CC}$ as the NSIs, 
any $\epsilon_{\ab} \sim 1$ will make the new matter effect be the same order as the SM effect.
Regarding the source of these new parameters, $\epsilon_{\ab}$ have the scale
\begin{align}
    \epsilon_{\ab} \propto \frac{m_W^2}{m_{\epsilon}^2} \sim \frac{10^{-2}}{m_\epsilon^2}\,
\end{align} 
in TeV, so the new interactions generated at a mass scale of $m_\epsilon = \SI{1}{TeV}$ will produce NSI parameters in the order of $10^{-2}$, 
two magnitudes below the SM matter effect. Thus, if we assume the new interactions to arise from a higher-energy theory at or above TeV scale, 
we then predict that the NSI parameters contribute at most $10^{-2}$ to the SM matter effect, decreasing quadratically.

>>>>

We have no independent sensitivity for the neither chirality nor flavor type of $\epsilon^X$, so we sum over these and study the effective matter NSI parameter
 $\epsilon_{\ab}$:
\begin{align}
    \epsilon_{\ab} = \sum_{X \in \{L,R\}} \sum_{f \in \{e,u,d\}} \frac{N_f}{N_e} \epsilon^{fX}_{\ab}\,.
\end{align}
Our matter study will be wholly confined to the interior of the Earth, where we assume electrical neutrality and equal distribution of neutrons and protons, 
we get $N_u/N_e \simeq N_d/N_e \simeq 3$. Also we assume the components $\epsilon_{\a\b}$ to be real. Thus,
\begin{align}
    \epsilon_{\ab} =  \sum_X [\epsilon_{\ab}^{eX} + 3(\epsilon_{\ab}^{uX} + \epsilon_{\ab}^{dX})]
\end{align}
Now, $\epsilon_{\ab}$ enters the Hamiltonian as entries of a potential-like matrix. In Eq.~\ref{eq:NSIH}, $A_{CC}\text{diag}(1,0,0)$ is our 
familiar matter potential from the Standard Model. There is also our new term, $A_{CC} \epsilon$, which contains the components $\epsilon_{\a\b}$:
\begin{align}\label{eq:NSIH}
    H &= \frac{1}{2E} \left[UM^2U^\dagger + A_{CC}\text{diag}(1,0,0) + A_{CC} \epsilon \right] \nonumber \\
      &= \frac{1}{2E} \left[UM^2U^\dagger + A_{CC}
      \begin{pmatrix}
          1 + \epsilon_{ee} & \epsilon_{e\mu} & \epsilon_{e\tau}  \\
          \epsilon_{\mu e} & \epsilon_{\mu\mu} & \epsilon_{\mu\tau}  \\
          \epsilon_{\tau e} & \epsilon_{\tau\mu} & \epsilon_{\tau\tau}
      \end{pmatrix} \right]\,.
\end{align} 
In the limit $\epsilon_{\ab} \to 0$, we recover the standard interaction Hamiltonian from Eq.~\ref{eq:H_3gen}.
We can draw several conclusions from this form of the Hamiltonian. Any nonzero off-diagonal element $\epsilon_{\ab}, \a \neq \b$ will make the NSI violate 
lepton flavor, just as the off-diagonal elements of $U$ does in the SM. Moreover, since the SM potential has the same order in $A_{CC}$ as the NSIs, 
any $\epsilon_{\ab} \sim 1$ will make the new matter effect be the same order as the SM effect.
Regarding the source of these new parameters, $\epsilon_{\ab}$ have the scale
\begin{align}
    \epsilon_{\ab} \propto \frac{m_W^2}{m_{\epsilon}^2} \sim \frac{10^{-2}}{m_\epsilon^2}\,
\end{align} 
in TeV, so the new interactions generated at a mass scale of $m_\epsilon = \SI{1}{TeV}$ will produce NSI parameters in the order of $10^{-2}$, 
two magnitudes below the SM matter effect. Thus, if we assume the new interactions to arise from a higher-energy theory at or above TeV scale, 
we then predict that the NSI parameters contribute at most $10^{-2}$ to the SM matter effect, decreasing quadratically.
